A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-17 article/04_Discussion.Rmd
some more discussion of representativity

>>>>

With regard to the primary variables *burial type* and *burial construction*, further special effects must be taken into account: The disturbance and robbery of graves was a widespread phenomenon in history and prehistory. Burial mounds were usually attacked more severely than flat graves due to their good visibility and could therefore be underrepresented in Radon-B. In many places they were also the subject of archaeological expeditions in the early days of archaeology at the end of the 19th and beginning of the 20th century. Of course, these excavations did not yield ^14^C-dates. Irrespective of this, it can be assumed that a large part of the burial mounds erected in the Bronze Age were destroyed by agricultural activity. This could also result in an under-representation of the archaeological findings [@hardingEuropeanSocietiesBronze2000a]. On the other hand, if a burial mound is still present, it is more easily visible and recognized by archaeologists today: Mounds are often clearly identifiable in aerial photographs or digital terrain models, while flat graves are much more difficult to identify for today's remote sensing methods. It is difficult to estimate the impact of these effects in detail, but an overrepresentation of mounds seems more likely than an overrepresentation of flat graves. The dating of cremation graves on bone remains methodically differs from the dating of body graves because it is based on the extraction of the mineral, not the organic, fraction in the bone [@lantingDatingCrematedBones2001]. The underlying chemical method was developed later, has only been used more frequently in the past 15 years and is associated with a number of particular difficulties [@olsenCharacterisationBlindTesting2008; @strydonck14CDatingCremated2009]. Burnt bone is generally more susceptible to weathering than unburned bone. An under-representation of cremation graves in current data collections is therefore more plausible - although this effect can only be observed to a very limited extent in Radon-B.
